Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-11 shanghai.tex

\section{The category of geometrized characters}\label{sec:category}

@@

@@

\section{Geometrized characters of commutative etale group schemes}

@@

\begin{proposition}\label{prop:etale}
  If $G$ is a commutative \'etale group scheme over $\Fq$ and
  $G(\bFq)$ is finitely generated then there is a canonical
  isomorphism
  \[
  \GCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, \Hom_\text{grp}(G(\bFq),\EEx)),
  \qquad \text{given by}\qquad
  [\cs{L}] \mapsto [\tau_\cs{L}],
  \]
  where $\tau_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
  \[
  \forall g\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(g) = \trFrob{\cs{L}}(g).
  \]
\end{proposition}

\begin{proof}
  To simplify notation, we set
  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EEx)$.  Recall the
  equivalence between etale group schemes over $\Fq$ and the category
  of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for
  the discrete topology on the group), given by $G \mapsto G(\bFq)$.
  Under this equivalence any geometrized character $\cs{L}=(\gcs{L},\mu,\phi)$
  on $G$ corresponds to:
  \begin{enumerate}
  \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
    $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over
    $G(\bFq)$;

  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
    $\mu_{x,y} \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
    for all $x,y \in G(\bFq)$, such that
    \[
    \begin{tikzcd}[row sep=40]
      \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
      && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
      \gcs{L}_{x} \otimes \gcs{L}_{y+z} \arrow{rr}{\id \otimes \mu_{y,z}}
      && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}
    \end{tikzcd}
    \]
    commutes, for all $x,y,z\in G(\bFq)$; and

  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} \ceq x^*\phi: \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
    such that
    \[
    \begin{tikzcd}[row sep=40]
      \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
      && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
      \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
      && \gcs{L}_x \otimes\gcs{L}_y
    \end{tikzcd}
    \]
    commutes, for all $x,y\in G(\bFq)$.
  \end{enumerate}
  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
  geometrized characters of $G$ corresponds to:
  \begin{enumerate}
  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
    of linear transformations (of one-dimensional $\EE$-vector spaces),
    as $x$ runs over $G(\bFq)$, such that
    \[
    \begin{tikzcd}[column sep=40]
      \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\varphi_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
      &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\varphi_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
      \gcs{L}_x \rar{\varphi_x} & \gcs{L'}_x
      & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y
    \end{tikzcd}
    \]
    both commute.
  \end{enumerate}
  It is clear that the category defined by conditions \ref{cs.0},
  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
  \cdef{$\GC(G(\bFq))$}, is equivalent to $\GC(G)$. We will prove the
  proposition by exhibiting an isomorphism between
  $\GCiso{G(\bFq)}$ and $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.

  To produce the isomorphism between $\GCiso{G(\bFq)}$ and
  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
  bundle $(\gcs{L},\mu)$, for each geometrized character $\cs{L}$ on $G$; 
  such a section exists by Lemma~\ref{lemma:section}.
  We will show that the group isomorphism does not depend on these
  choices.
%
  We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(\Weil{\Fq},G(\bFq)^*)$
  as follows. Recall that $\cs{L}$ also determines a family of linear transformations
  $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
  spaces, so $\phi_x(s(\Frob{\Fq}(x)))$ is a scalar multiply of $s(x)$, for
  each $x\in G(\bFq)$; let $\tau_\cs{L}(\Frob{\Fq})(x)$ be that scalar, so
  \begin{equation}\label{t}
    \forall x\in G(\bFq),\qquad \phi_{x}(s(\Frob{\Fq}(x)) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
  \end{equation}
  Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
  the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces
  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$,
  for all $x,y \in G(\bFq)$.
  % \Clifton{The alternative to this approach is to change the
  %   definition of geometrized characters to incorporate the notion of
  %   Galois sheaves. That might not be so bad, but would add another
  %   layer of complication, which we wouldn't use profitably, expect
  %   here.}

  Now $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ is defined, recursively, by
  $\tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1})$,
  where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
  to pointwise multiplication of functions. This gives
  \[
  \obj \GC(G(\bFq)) \longrightarrow Z^1(\Weil{\Fq},G(\bFq)^*),
  \qquad \text{defined by} \qquad \cs{L} \mapsto \tau_\cs{L}.
  \]

  Although we used a global section $s_\cs{L}$ in the definition of
  $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
  choice. To see why, let $s_1$ and $s_2$ be two global sections of
  the line bundle $(\gcs{L},\mu)$, in the sense above and let $\tau_1$
  and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$, respectively,
  as above. Since, for each $x\in G(\bFq)$, $\gcs{L}_x$ is a
  one-dimensional $\EE$-vector space, there is a unique scalar
  $a(x) \in \EE$ such that $s_2(x) = a(x) s_1(x)$; moreover, $a(x)$ is
  non-zero, since $s_2(x)$ is non-zero. Then \eqref{section} and
  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
  $a\in G(\bFq)^*$. Now consider the coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$. Then $\tau_2 = \tau_0 \tau_1$,
  so $\tau_2$ and $\tau_1$ are cohomologous. In this way we see that
  \begin{equation}\label{cohomologous}
    \obj \GC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
    \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
  \end{equation}
  is independent of the choice of global sections made above.

  We now show that the function $\obj \GC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*)$
  factors through $\obj \GC(G(\bFq)) \to \GCiso{G(\bFq)}$.
  To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
  $\tau$ and $\tau'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EEx$
  by $\varphi_x(s(x)) = \phi(x) s'(x)$. 
  \Clifton{Notation problem here: replace $\phi$ with something else.}
  By the second part of condition~\ref{cs.3},
  $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\phi \cdot \phi^{-1})$,
  so $\tau$ and $\tau'$ are cohomologous. This concludes the definition of
  \begin{equation}\label{pich1}
    \GCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [\tau_\cs{L}].
  \end{equation}
  Now it follows from \eqref{t} that the image of the isomorphism
  class of $\cs{L}$ is indeed represented by a cocycle $\tau_\cs{L}$ such
  that $\tau_\cs{L}(\Frob{\Fq}) = \trFrob{\cs{L}}$ on $G(\Fq)$, which is to
  say, when evaluated at $\Frob{\Fq}$, the cocycle $\tau_\cs{L}$ is an
  extension of the trace of Frobenius of $\cs{L}$.

  It only remains to show that \eqref{pich1} is a group
  isomorphism. This is straightforward.
  \Clifton{Straightforward, yes, but it still needs to be written down here.}
\end{proof}

\begin{lemma}\label{lemma:section}
 If $\cs{L}$ is a geometrized character then there is a non-trivial section of $\gcs{L}$ 
 compatible with $\mu$ in the sense that 
 \begin{equation}\label{section}
  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
 \end{equation}
\end{lemma}

\begin{proof}
First, however, we show that such global sections exist.  Since
  $G(\bFq)$ is finitely-generated abelian, it admits a decomposition
  $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such
  that $G(\bFq)_\text{tors}$ is finite.  Let $x_1, \ldots , x_r$ be a
  basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let
  $y_1, \ldots , y_t$ be a generators for the torsion part of
  $G(\bFq)$ corresponding to the decomposition
  $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with
  $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$;
  for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set
  $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. ....
  \todo{under construction}
  In this way we define a section
  $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of
  projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that
  $\mu_{x,y}(s(x+y)) = s(x)\otimes s(y)$ for all $x,y \in G(\bFq)$.
  Under the equivalence at the beginning of this section, $s = s_\cs{L}$
  corresponds to a global section of the line bundle $(\gcs{L},\mu)$.

\Clifton{I'm going to remove all mention of line bundles from this paper.}
\end{proof}

>>>>

\section{Notation}

@@

For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.

\section{The category of geometrized characters}\label{section:category}

@@

\section{Geometrized characters of commutative \'etale group schemes}

@@

\'Etale group schemes form a counterpoint to connected groups, since the component group
is always \'etale.  The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
between the category of \'etale group schemes over $\Fq$ and the category of groups equipped
with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.

For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, we define a category of geometrized characters $\GC(G(\bFq))$.
An object in $\GC(G(\bFq))$ is given by the data of

\begin{enumerate}
 \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
  $G(\bFq)$;

 \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
  $\mu_{x,y} : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
  for all $x,y \in G(\bFq)$, such that
  \[
   \begin{tikzcd}[row sep=40]
    \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
    && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
    \gcs{L}_{x} \otimes \gcs{L}_{y+z} \arrow{rr}{\id \otimes \mu_{y,z}}
    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}
   \end{tikzcd}
  \]
  commutes, for all $x,y,z\in G(\bFq)$; and

 \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
  such that
  \[
   \begin{tikzcd}[row sep=40]
    \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
    && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
    && \gcs{L}_x \otimes\gcs{L}_y
   \end{tikzcd}
  \]
  commutes, for all $x,y\in G(\bFq)$.
\end{enumerate}

A morphism $\varphi : \cs{L} \to \cs{L'}$ is given by 
\begin{enumerate}
 \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x : \gcs{L}_x \to \gcs{L'}_x$
  of linear transformations (of one-dimensional $\EE$-vector spaces),
  as $x$ runs over $G(\bFq)$, such that
  \[
   \begin{tikzcd}[column sep=40]
    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\varphi_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\varphi_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
    \gcs{L}_x \rar{\varphi_x} & \gcs{L'}_x
    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y
   \end{tikzcd}
  \]
  both commute.
\end{enumerate}

The functor $\GC(G) \to \GC(G(\bFq))$ defined by
$(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, \phi_x = x^*\phi)$
is easily seen to be an equivalence.  We may now define a \cdef{global section}
of a geometrized character $\cs{L}$ on an \'etale group scheme $G$ as a choice $s(x) \in \gcs{L}_x$ for every
$x \in G(\bFq)$, satisfying
 \begin{equation}\label{section}
  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
 \end{equation}

\begin{lemma}\label{lemma:section}
 If $\cs{L}$ is a geometrized character on a commutative, \'etale group scheme $G$
 with $G(\bFq)$ finitely generated then nontrivial global sections of $\cs{L}$ exist.
\end{lemma}

\begin{proof}
  Since $G(\bFq)$ is a finitely-generated abelian group, it admits a decomposition
  \[
  G(\bFq) \iso \ZZ^r \oplus \bigoplus_{j=1}^t \ZZ / m_j \ZZ;
  \]
  let $x_1, \ldots, x_r, y_1, \ldots, y_t$ be a corresponding set of generators of $G(\bFq)$.
  We will define a section $s$ by choosing values on these generators and extending to all
  of $G(\bFq)$ through \eqref{section}.

  There is a unique isomorphism $\gcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
  to the multiplication map $\EE \otimes \EE \to \EE$.
  The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
  then forces $s(0) = 1$.

  The $\mu_{x,y}$ yield an isomorphism $\alpha_j : \gcs{L}_{y_j}^{\otimes m_j} \to \gcs{L}_0$.
  An initial nonzero choice of $s(y_j)$ need only be scaled by $\alpha_j(s(y_j))^{-1/m_j}$ in order to map to
  $1$ under this isomorphism.  Since compatibility under the $\alpha_j$ are the only constraints on the
  $s(x_j)$ and $s(y_j)$, global sections exist.
\end{proof}

These global sections will allow us to construct the isomorphism in the following proposition.

\begin{proposition}\label{prop:etale}
  If $G$ is a commutative \'etale group scheme over $\Fq$ and
  $G(\bFq)$ is finitely generated then there is a canonical
  isomorphism
  \[
  \GCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
  \qquad \text{given by}\qquad
  [\cs{L}] \mapsto [\tau_\cs{L}],
  \]
  where $\tau_\cs{L}: \Weil{\Fq}\to G(\bFq)^*$ is a cocycle such that
  \[
  \forall x\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(x) = \trFrob{\cs{L}}(x).
  \]
\end{proposition}

\begin{proof}
  Suppose $\cs{L}$ is a geometrized character on $G$.  Using Lemma~\ref{lemma:section}, we may choose a global section $s_{\cs{L}}$
  of $\cs{L}$.  We will construct a group isomorphism between $\GCiso{G(\bFq)}$ and
  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s_{\cs{L}}$, then prove independence from the choice of section.

  Starting from $\cs{L}$, we define a cocyle $\tau_{\cs{L}} \in Z^1(\Weil{\Fq},G(\bFq)^*)$ as follows.
  For $x \in G(\bFq)$, $\cs{L}$ determines an isomorphism $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
  of one-dimensional $\EE$-vector spaces; define $\tau_\cs{L}$ by
  \begin{equation}\label{t}
   \phi_{x}(s(\Frob{\Fq}(x))) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
  \end{equation}
  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $t_\cs{L}(x)$, so the restriction of
  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $t_\cs{L}$.
  In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
  the scalar $\tau_\cs{L}(\Frob{k})(x)$ is non-zero.  Moreover, condition~\ref{cs.1} forces
  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$
  for all $x,y \in G(\bFq)$.  Now define $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ recursively by
  \[
   \tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1}),
  \]
  where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
  to pointwise multiplication of functions.

  Although we used a global section $s_\cs{L}$ in the definition of
  $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
  choice. To see why, let $s_1$ and $s_2$ be two global sections of
  $\cs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
  For each $x \in G(\bFq)$ there is a unique scalar
  $a(x) \in \EEx$ such that $s_2(x) = a(x) s_1(x)$. Then \eqref{section} and
  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
  \begin{equation}\label{cohomologous}
    \obj \GC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
    \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
  \end{equation}
  is independent of the choice of global sections made above.

  We now show that $[\tau_\cs{L}]$ depends only on the isomorphism class of $\cs{L}$.
  Let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
  $\tau$ and $\tau'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
  non-zero scalar multiple of $s'(x)$; define $\delta: G(\bFq) \to \EEx$
  by $\varphi_x(s(x)) = \delta(x) s'(x)$.
  By the second part of condition~\ref{cs.3},
  $\delta(x+y) = \delta(x)\delta(y)$, so $\delta \in G(\bFq)^*$. By the first part of
  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\delta \cdot \delta^{-1})$,
  so $\tau$ and $\tau'$ are cohomologous. This concludes the definition of
  \begin{equation}\label{pich1}
    \GCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*).
  \end{equation}

  It only remains to show that \eqref{pich1} is a group
  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two geometrized characters.
  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes s'$ is a global section for
  $\cs{L} \otimes \cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes \cs{L}'$ imply that
  $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$.

  \Clifton{Straightforward, yes, but it still needs to be written down here.}
\end{proof}
